Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-07 longSC.tex
adopting ante's

\subsection{Higher Order Harmonic Correlations}
\label{sec:theory_highorder}
The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical model calculations. 
The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~\ref{fig:Figure_5}. 
While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations better are compared to the results of higher order harmonic correlations. The other calculations show a quite clear deviation from the data. 
As it is seen in Fig.~1 from Ref.~\cite{Niemi:2015qia} that the temperature at the minimum of $\eta/s$ for "\textit{param1}" (at $T$ = 150~MeV) is smaller than the other parameters used. The model calculations with the parameters whose temperature at the minimum of $\eta/s$ is larger than "param1" can be ruled out.
As shown in Fig.~\ref{fig:Figure_5}, the correlations between $v_5$ and $v_2$ and between $v_5$ and $v_3$ are well described by those two model parameters within errors.  The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$. 
In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the data significantly like the correlation between $v_3$ and $v_2$.

%\begin{figure*}[!]
%            \begin{center}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT.eps}}
%                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT.eps}}
%                \end{center}
%        \caption{Measurements of  SC(3,2) and SC(4,2) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
%        \label{fig:Figure_5_0}
%\end{figure*}

\begin{figure*}[!]
            \begin{center}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_EKRT.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_EKRT.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_EKRT.eps}}
              \end{center}
        \caption{Measurements of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
        \label{fig:Figure_5}
\end{figure*}

@@

The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_8}.
As it has been discussed in Sec~\ref{sec:theory_loworder}, NSC(3,2) is underestimated by the hydrodynamic calculations. 
The hydrodynamic calculations show very weak $p_{\rm T}$ dependence for NSC(3,2) and a moderate $p_{\rm T}$ dependence for NSC(4,2).
The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations except for the centrality range 40-50\% where the correlation strength gets stronger with increasing $p_{\rm T}$. 
In the case of NSC(4,2), the $p_{\rm T}$ dependence is well described in all centrality ranges reported.

>>>>

\subsection{Higher Order Harmonic Correlations}
\label{sec:theory_highorder}
The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical model calculations. 
The event-by-event EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~\ref{fig:Figure_5}. 
While we discussed the comparison to these hydrodynamic model calculations with various temperature dependent $\eta/s$ parameterizations, only two calculations with the parameters which describe the lower order harmonic correlations best are compared to the results of higher order harmonic correlations. 
As it can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for ''param1'' parameterization the phase transition from hadronic to QGP phase occurs at lowest temperature, already around 150~MeV. This parameterization is also characterized with moderate slope of $\eta/s(T)$ of decreasing (increasing) in hadronic (QGP) phase.
The model calculations with the parameters for which the temperature of phase transition is larger than for ``param1`` can be ruled out already with the previous measurement~\cite{ALICE:2016kpq}.
As shown in Fig.~\ref{fig:Figure_5}, only the correlations between $v_5$ and $v_2$ are well described for all available centralities. 
On the other hand, for correlations between $v_5$ and $v_3$ the description fails in the transition towards more peripheral collisions, providing further independent constraints for the models.
%The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$. 
In the case of the correlation between $v_4$ and $v_3$, the same models underestimate the data significantly.
Most notably, this measurement is so far the most dramatic example of a failure of constant $\eta/s$ to describe the data.

\begin{figure*}[!]
            \begin{center}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC32_EKRT.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC42_EKRT.eps}}
                \end{center}
        \caption{Measurements of  SC(3,2) and SC(4,2) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with $\eta/s(T)$ parameterizations~\cite{Niemi:2015qia}.}
        \label{fig:Figure_5_0}
\end{figure*}

\begin{figure*}[!]
            \begin{center}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC52_EKRT.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC53_EKRT.eps}}
                       \resizebox{0.32\textwidth}{!}{\includegraphics{figs/fig3_QConly_ModelComparison_SC43_EKRT.eps}}
              \end{center}
        \caption{Measurements of  SC(5,2), SC(5,3) and SC(4,3) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}}        \label{fig:Figure_5}
\end{figure*}

@@

The event-by-event EKRT+viscous hydrodynamic calculations are compared to the data in Fig.~\ref{fig:Figure_8}.
As it has been discussed in Sec~\ref{sec:theory_loworder}, NSC(3,2) is underestimated by the hydrodynamic calculations. 
The hydrodynamic calculations show very weak $p_{\rm T}$ dependence for NSC(3,2) and a moderate $p_{\rm T}$ dependence for NSC(4,2).
The $p_{\rm T}$ dependence of NSC(3,2) is well described by the model calculations except for the centrality range 40-50\% where the correlation strength gets stronger with increasing $p_{\rm T}$. 
In the case of NSC(4,2), the $p_{\rm T}$ dependence is well described in all centrality ranges.
